Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/Motiv.tex

Our overall goal is to 
(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of \Sadegh{an additional bounded
disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);}
and at the same time
%\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
(ii) to minimize the total number of bits that are required for storing the explicit controller.

@@

Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
\Sadegh{
We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
\begin{equation}
\mathcal W_{\Delta} := \{w_1+w_2 \,|\, w_1\in \mathcal W, \|w_2\|\le \Delta\}
\quad\text{ for all } \Delta\ge 0.
\end{equation}
 }

 \Sadegh{
For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. Over the computed controller, we compute the error due to incorrect region selection $e$ and in case that $e<\Delta$, we ask Daisy
to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
at all points in the control domain, the difference between the infinite-precision controller function
and its mixed-precision implementation is at most $\Delta_0$.
}

\Sadegh{
Unfortunately, $\Delta_0=0$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has $14$ regions.
\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps} 
}
%\begin{equation}
%\kappa(x_k)=
%\begin{cases}
%.05x_k-9.67 & \text{if $x_k\in \mathcal{R}_1$}\\
%F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
%\vdots\\
%F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
%\end{cases} 
%\end{equation}

>>>>

Our overall goal is to 
(i) design a robust MPC controller that achieves the performance objectives including hard constraints in spite of an additional bounded
disturbance $\Delta$ modeling the implementation error (both errors due to choosing a wrong region and the finite-precision computation of the control action);
and at the same time
%\eva{what about the modelling error that $\Delta$ bounded in the paragraph before?}
(ii) to minimize the total number of bits that are required for storing the explicit controller.

@@

Figure \ref{fig:overview} gives a high-level overview of our proposed setup.
We start by selecting an initial bound $\Delta_0$ on the implementation error and enlarge $\mathcal W$ with $\Delta_0$ as $\mathcal W_{\Delta_0}$, where
\begin{equation}
\mathcal W_{\Delta} := \{w_1+w_2 \,|\, w_1\in \mathcal W, \|w_2\|\le \Delta\}
\quad\text{ for all } \Delta\ge 0.
\end{equation}

For our example, we choose $\Delta_0=0.01$ and $\mathcal W = \{0\}$. 
We use MATLAB to find a robust explicit MPC with disturbance set $\mathcal W_{\Delta_0}$. Over the computed controller, we compute the error due to an incorrect region selection $e$ and in case that $e<\Delta_0$, we ask Daisy
to provide a mixed-precision scheme such that the associated implementation error is at most $\Delta_0$, that is,
at all points in the control domain, the difference between the infinite-precision controller function
and its mixed-precision implementation is at most $\Delta_0$.

Unfortunately, $\Delta_0=0.01$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has $14$ regions.
\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}

%\begin{equation}
%\kappa(x_k)=
%\begin{cases}
%.05x_k-9.67 & \text{if $x_k\in \mathcal{R}_1$}\\
%F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
%\vdots\\
%F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
%\end{cases} 
%\end{equation}
